Transforming Trash as an Artistic Act

### 2015-11-22 chapter2.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

In this chapter trash (and the practice of transforming trash) is examined in theoretical (and conceptual) aspect. Theoretical foundations of trash are discussed. (Further benefited from historical and social aspect of trash. (?)) How do scholars conceptualized the trash? What do they say about it?

Trash draws attention of many scholars and people who are professional in different areas. Further trash is a common topic(problem?) of the all ages through the human history. In other words this topic is not introduced in recent years (or ages). It always part of the human practice and life. Even if trash is refused and discarded thing, there are people giving attention to them.

%%%
%%%
%%%
\section{Throw away culture}
We need to ask what is the source of trash.

Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?) Behavioral pattern of throw away culture results in the trash. (This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.

@@

%%% Reference from Identity, mobility and the throwaway society
\todo{we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)}

\quotes{In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society. In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new. Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act. The thesis, however, lacks depth and provenance. It is, actually, glib. Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
% In this paper criticized the perception of throw away culture and arguments. They show the weak points of the arguments. What I understand from trow away culture?

In the scope of this thesis increasing consumption is motivator (draws attention more) but it does not bind to this. Always needed to keep in my mind that the practice of discard does not exist on only current societies.

Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundereds of disposible containers and materials bt the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."

\todo{throw away sprit}

Industrial age played significant role (engine of the mountains of rubbish.)

@@

% Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor.

% COFFEE CUP / Transforming them and invite other people, reveals its process.
% FROM http://www.gwynethleech.com/public-drawing/cup-windows/statement
  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup5.jpg}
      \caption[Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions Variable]{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. For ArtPrize I am showing 1001 of my cup artworks, each representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.}
      \label{fig:GwynethLeech_TheCup}
  \end{figure}

  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup3.jpg}
      \caption[Gwyneth Leech while painting in the public]{There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many placas and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world.}
      \label{fig:GwynethLeech_InAction}
  \end{figure}

% Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz.

% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/rubysilvious-teabag-Day237.jpg}
      \caption[Ruby Silvious, 363 Days of Tea, Day 237, 2015, Mixed media on upcycled paper tea bags, Dimensions Variable]{In the beginning of this year, visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.}
      \label{fig:RubySilvious_TeaBag}
  \end{figure}

%****************************************
% Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels. Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.

% Potraits of Global Mass culture from Chris Jordan. In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.”

% Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits

% Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor.

% He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.

% Chris jordan hem bir gerçeği açığa çıkarıyor. 
% Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.
%........................................

@@

% Aslında şöyle bir şey var mustafa, aslında sanatçının yaptığı şey ürünlerinden çok tekrar ve devamlı olarak eyleme geçirdiği yaklaşımı. Çöpün de bu tekrar eden yapısı buna uyum sağlıyor. Çünkü zaten hatayın sürekli bir parçası. Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.
%........................................

%****************************************
% Tracy emin mesela. Yani aslında bir şekilde bir yandan aslında teoriye mi değiniyorum yoksa sanatçıların işlerine mi değiniyorum, bunların teorideki karşılıklarını mı buluyorum emin olamadım. Bunların ikisi paslaşarak ilerliyor aslında. Aslında çöplerin bize ait çok şeyler söylediğini ünlülerin çöplerini karıştıran yaklaşım ortaya çıkarıyor. Bu işde bununla ilgili aslında.
%........................................

@@

% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/ChrisJordan-Albatross.jpg}
      \caption[Chris Jordan, Albatross at Midway Atoll Refuge, 2009]{The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.}
      \label{fig:ChrisJordan_Albatross}
  \end{figure}

@@

\comment{WALL-E belki olabilir. Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir. Çöp dağları, çöp denizleri. Atılmış binbir türlü nesne. ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor. Bundan basetmişken aslında pressleme işi yapan şu cesar. Bu şekilde olmak zorunda mı? Bunun alternatifi yok mu? Aslında bu tezde bunlara cevap bulunabilir. Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var. Ya da başka neler var? Bunları araştıran inceleyen bir yazı. Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz. İnsanlık buna mı dönüşücek? Başka bir ihtimal yok mu? Gerçekten de dünyayı bekleyen şey bu mu? Bir çöp yığını olması mı? Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?}

\comment{WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles giant dozers that moves and piles trash in the landfills. This robot creates squeezed trash blocks that have no meaning and interpretation. All different objects in terms of their physical and social properties turned to same squeezed garbage blocks. There are mountains of trash and place is very limited. By squeezing them, WALL-E saves space. \todo{What is the context of it? Which part is related with my topic?} What are we going to do with all these mountains of trash? \todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.}

@@

\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects. It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.

@@

\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)

@@

\textbf{Motivations and found object practice:}
\begin{itemize}
\item Discovery and engagement
  \begin{itemize}
  \item Seeking out: The adventure of hunting
  \item Finding the unexpected
  \item The location of discovery
  \item Metamorphosis and transformation: Imagining a use for the object
  \item Creative action
  \end{itemize}
\item History and time past
  \begin{itemize}
  \item Trigger of personal memories
  \item The object’s story: Reflection about earlier “life” of object and previous owner
  \item Capturing something elusive: Making sense of an unknown past
  \end{itemize}
\item The symbolic and functional object
  \begin{itemize}
  \item Aesthetic properties: Visual, tactile, original
  \item Cost: The thrill of a free find
  \item Evocative: More interesting than something new
  \item Useable solutions for practical problems
  \end{itemize}
\item Psychological processes
  \begin{itemize}
  \item Personal resourcefulness
  \item Impact on memory, emotion, cognition
  \item Meaningfulness of object
  \item Arouses interest: Motivates
  \item Social engagement
  \end{itemize}
\item Ecological affirmation
  \begin{itemize}
  \item Environmental concerns
  \item Against the cult of the new: Slowing down consumption
  \item Transforming rubbish
  \end{itemize}
\end{itemize}

@@

Results of this study also support consideration of found objects as important artifacts that are signifiers of cultural meaning.

[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials. So what is value?]
\textbf{Value.}
\begin{itemize}
\item n. relative worth, merit, or importance: the value of a college education; the value of a queen in chess.
\item n. monetary or material worth, as in commerce or trade: This piece of land has greatly increased in value.
\item n. estimated or assigned worth; valuation: a painting with a current value of \$500,000.
\item Value is that quality of anything which renders it desirable or useful: the value of sunlight or good books. Worth implies especially spiritual qualities of mind and character, or moral excellence: Few knew her true worth.
\item the desirability of a thing, often in respect of some property such as usefulness or exchangeability; worth, merit, or importance
\end{itemize}

%%%
%%%
%%%
\section{Summary}
\begin{itemize}
\item Shared practice through the different ages of humanity and different societies. 
\item Moving nature of trash/objects.
\item Classification is the main key, trash is not related with the object property. 
\item Value creation, shifts in the society. 
\item Trash has archaeological value.
\item Trash has potential to be used again.
\end{itemize}

>>>>

In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash are discussed. Further benefited from historical and social aspect of trash. It is questioned that how do scholars conceptualized the trash, what do they say about it?

Firstly we need to ask what is the source of trash. How is it generated? Secondly \ldots

%%%
%%%
%%%
\section{Throw away culture}
%%% Reference from Identity, mobility and the throwaway society
The term is actually a criticism of over consumption of short-live disposable objects.
\todo[inline]{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere. Even if conducted a qualitative research people are really do not throw away their things. \paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}. They analyzed the things like television, furniture and toys like that.

\comment{Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?)}

@@

\paraphrase{In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new. Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act. The thesis, however, lacks depth and provenance. It is, actually, glib. Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}

\comment{zaten zengin olanın atma lüksü var.}

\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} Therefore Industrial age played significant role (engine of the mountains of rubbish.)

@@

\comment{All around of us filled with the things that are disposable. They are part of our daily activities.}

% not easily understandable with the entering non-art objects in art. artist are responding the current societies habits in a different ways. what they are doing here is to see other possibliteis and show actually what is going on. what does it mean all of these things.

\todo[inline]{Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor. Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz. Bir anlamda çöplerin sanatçıların günlüklerine dönüştüklerini görüyoruz. Yani bir dönüşüm var. Benzer bir şey her gün yapılan işin fotoğrafını çeken insanda da var. Günlük rutinleri çöp üzerinden yakalayanlar var.}

\todo{need to elaborate}

% ARTWORK
% COFFEE CUP
% FROM http://www.gwynethleech.com/
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
  \caption{Installation view}
  \label{fig:GwynethLeech_Installation}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
  \caption{Painting in the public}
  \label{fig:GwynethLeech_Public}
\end{subfigure}
\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
\label{fig:GwynethLeech_CoffeeCups}
\end{figure}

I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transform its cup.

% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
  \label{fig:RubySilvious_TeaBag}
\end{figure}

Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.

\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. Portraits of Global Mass culture from Chris Jordan. In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.
\todo[inline]{Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor. Chris jordan hem bir gerçeği açığa çıkarıyor. Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.}

@@

% Aslında şöyle bir şey var mustafa, aslında sanatçının yaptığı şey ürünlerinden çok tekrar ve devamlı olarak eyleme geçirdiği yaklaşımı. Çöpün de bu tekrar eden yapısı buna uyum sağlıyor. Çünkü zaten hatayın sürekli bir parçası. Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.

% Sanatçıların işlerine bir de bu açıdan baktığımızda ne görüyoruz.
%........................................

\comment{Things that are thrown away are one side of it. Actually all of our waste tells about us. ref required. Meaning of waste and what it tells about us. Understanding people through their wastes. REF. Tracey Emin's work. She opens up her wastes and also her life.}

% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
\comment{GARBOLOGY} Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris. \todo[inline]{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}

% Garbology, from Encyclopedia, Abhijit Roy
\paraphrase{"The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. A. J. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."}\todo{ref.}

% Rubbish: The Archeology of Garbage, p.24
\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades. The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life. (example of Medical researches)} \todo{ref.}

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
  \caption{Tracey Emin, My Bed, 1998}
  \label{fig:TraceyEmin_MyBed}
\end{figure}

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. It is a time capsule. The cigarettes that litter the floor will one day no longer exist; neither will the newspapers. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo[inline]{Dört günden beri yataktan çıkmamış. İşte o sürede birikenler.}

@@

% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
  \label{fig:ChrisJordan_Albatross}
\end{figure}

The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.

@@

%\comment{WALL-E belki olabilir. Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir. Çöp dağları, çöp denizleri. Atılmış binbir türlü nesne. ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor. Bundan basetmişken aslında pressleme işi yapan şu cesar. Bu şekilde olmak zorunda mı? Bunun alternatifi yok mu? Aslında bu tezde bunlara cevap bulunabilir. Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var. Ya da başka neler var? Bunları araştıran inceleyen bir yazı. Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz. İnsanlık buna mı dönüşücek? Başka bir ihtimal yok mu? Gerçekten de dünyayı bekleyen şey bu mu? Bir çöp yığını olması mı? Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?}

%\comment{WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles giant dozers that moves and piles trash in the landfills. This robot creates squeezed trash blocks that have no meaning and interpretation. All different objects in terms of their physical and social properties turned to same squeezed garbage blocks. There are mountains of trash and place is very limited. By squeezing them, WALL-E saves space. \todo{What is the context of it? Which part is related with my topic?} What are we going to do with all these mountains of trash? \todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.}

@@

\subsubsection{The Practices: From Rubbish to Durable}
Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects. It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.

@@

\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.) Maybe publicly exhibiting them.

@@

\todo[inline]{table moved to drafts.}

@@

Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.

%%%
%%%
%%%
\section{Summary}
\begin{itemize}
\item Moving nature of trash/objects.
\item Classification is the main key, trash is not related with the object property. 
\item Value creation, shifts in the society. 
\item Trash has archaeological value.
\item Trash has potential to be used again.
\end{itemize}
